Twists of supersymmetric gauge theories

### 2019-08-16 paper.tex
Started editing the 8d twists section

In the next term, \ref{MC_2}, the first two summands vanish by Lemma \ref{SUSY_rotation_invariance_lemma}, and the last two summands vanish by Lemma \ref{onshell_interaction_lemma}.  Likewise, in term \ref{MC_3}, the first two summands vanish by Lemma \ref{SUSY_rotation_invariance_lemma}, and the last term vanishes by applying the 3-$\psi$ rule, Theorem \ref{3_psi_thm}.  Indeed, we expand
\begin{align*}
 \{I^{(1)}, I^{(2)}\}  &= \left\{\langle A^* , \Gamma(Q_3, \lambda)\rangle, \left\langle\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right\rangle\right\}\\
 &= \left\langle A^*\;,\; \Gamma\left(Q_3, \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right)\right\rangle + \\
 &\quad + \left\langle\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2))\rho(A^*)Q_3 + \frac 12 \left( (Q_2, \rho(A^*)Q_3)Q_1 + (Q_1, \rho(A^*)Q_3)Q_2 \right)\right\rangle \\
 &= \left\langle A^*\;,\; \Gamma\left(Q_3, \rho(\Gamma(Q_1,Q_2)) \lambda^*\right)\right\rangle +  \left\langle\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2))\rho(A^*)Q_3\right\rangle + \\
 &\quad + (Q_2, \lambda^*)\langle A^*, \Gamma(Q_3, Q_1)\rangle + (Q_1, \lambda^*)\langle A^*, \Gamma(Q_3, Q_2)\rangle,
\end{align*}
where we used, on the last line, the fact that $(Q, \rho(v)Q') = \langle v, \Gamma(Q, Q')\rangle$.  We can simplify this expression by manipulating the second summand.  Indeed,
\begin{align*}
\left\langle\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2))\rho(A^*)Q_3\right\rangle &= - \left\langle\lambda^* \;,\; \rho(A^*)\rho(\Gamma(Q_1,Q_2))Q_3\right\rangle - \langle A^*, \Gamma(Q_1,Q_2) \rangle (\lambda^*, Q_3) \\
&= - \left\langle A^*\;,\; \Gamma\left(Q_3, \rho(\Gamma(Q_1,Q_2)) \lambda^* \right)\right\rangle + \langle A^*, \Gamma(Q_1,Q_2) \rangle (Q_3, \lambda^*)
\end{align*}
since \chris{The equality of the first terms looks write when I write it in indices, not sure how to write it coordinate freely.  Also not sure of the sign of the second term.}.
We therefore conclude that the bracket $\{I^{(1)}, I^{(2)}\}$ is the $(123)$-symmetrization of the expression 
\[(Q_1, \lambda^*)\langle A^*, \Gamma(Q_2, Q_3)\rangle = \langle A^*, (\Gamma(Q_1,\rho(\Gamma(Q_2,Q_3))\lambda^*) + \Gamma(\lambda^*,\rho(\Gamma(Q_2,Q_3))Q_1))\rangle,\]
which vanishes by applying Theorem \ref{3_psi_thm} to the two expressions on the right-hand side \chris{This doesn't work: it's only applicable to kill the second term.}.
\chris{Ok, in earlier notes Pavel claimed that this bracket was the $(123)$-symmetrization of 
\[\langle A^*, \Gamma(Q_1, \rho(\Gamma(Q_2,Q_3))\lambda^*\rangle + (Q_1,\lambda^*)(A^*, \Gamma(Q_2,Q_3)).\]
I don't see that here -- is that true?  I might be missing something.}.

@@

\chris{There is a single non-zero class of square zero supercharges in 9d, which are minimal (i.e. have 5d image).  They are stabilized by $\SU(4)$.  The twisted theory is only $\ZZ/2\ZZ$-graded.}

@@

\subsection{Dimension 8}

>>>>

In the next term, \ref{MC_2}, the first two summands vanish by Lemma \ref{SUSY_rotation_invariance_lemma}, and the last two summands vanish by Lemma \ref{onshell_interaction_lemma}.  Likewise, in term \ref{MC_3}, the first two summands vanish by Lemma \ref{SUSY_rotation_invariance_lemma}, and the last term vanishes by applying the 3-$\psi$ rule, Theorem \ref{3_psi_thm}.  Indeed, we expand
\begin{align*}
 \{I^{(1)}, I^{(2)}\}  &= \left\{\langle A^* , \Gamma(Q_3, \lambda)\rangle, \left\langle\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right\rangle\right\}\\
 &= \left\langle A^*\;,\; \Gamma\left(Q_3, \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right)\right\rangle + \\
 &\quad + \left\langle\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2))\rho(A^*)Q_3 + \frac 12 \left( (Q_2, \rho(A^*)Q_3)Q_1 + (Q_1, \rho(A^*)Q_3)Q_2 \right)\right\rangle \\
 &= \left\langle A^*\;,\; \Gamma\left(Q_3, \rho(\Gamma(Q_1,Q_2)) \lambda^*\right)\right\rangle +  \left\langle\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2))\rho(A^*)Q_3\right\rangle + \\
 &\quad + (Q_2, \lambda^*)\langle A^*, \Gamma(Q_3, Q_1)\rangle + (Q_1, \lambda^*)\langle A^*, \Gamma(Q_3, Q_2)\rangle,
\end{align*}
where we used, on the last line, the fact that $(Q, \rho(v)Q') = \langle v, \Gamma(Q, Q')\rangle$.  We can simplify this expression by manipulating the second summand.  Indeed,
\begin{align*}
\left\langle\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2))\rho(A^*)Q_3\right\rangle &= - \left\langle\lambda^* \;,\; \rho(A^*)\rho(\Gamma(Q_1,Q_2))Q_3\right\rangle - \langle A^*, \Gamma(Q_1,Q_2) \rangle (\lambda^*, Q_3) \\
&= - \left\langle A^*\;,\; \Gamma\left(Q_3, \rho(\Gamma(Q_1,Q_2)) \lambda^* \right)\right\rangle + \langle A^*, \Gamma(Q_1,Q_2) \rangle (Q_3, \lambda^*)
\end{align*}
since \chris{The equality of the first terms looks right when I write it in indices, not sure how to write it coordinate freely.  Also not sure of the sign of the second term.}.
We therefore conclude that the bracket $\{I^{(1)}, I^{(2)}\}$ is the $(123)$-symmetrization of the expression 
\[(Q_1, \lambda^*)\langle A^*, \Gamma(Q_2, Q_3)\rangle = \langle A^*, (\Gamma(Q_1,\rho(\Gamma(Q_2,Q_3))\lambda^*) + \Gamma(\lambda^*,\rho(\Gamma(Q_2,Q_3))Q_1))\rangle,\]
which vanishes by applying Theorem \ref{3_psi_thm} to the two expressions on the right-hand side \chris{This doesn't work: it's only applicable to kill the second term.}.
\chris{Ok, in earlier notes Pavel claimed that this bracket was the $(123)$-symmetrization of 
\[\langle A^*, \Gamma(Q_1, \rho(\Gamma(Q_2,Q_3))\lambda^*\rangle + (Q_1,\lambda^*)(A^*, \Gamma(Q_2,Q_3)).\]
I don't see that here -- is that true?  I might be missing something.}.

@@

There is a single non-zero equivalence class of square zero supercharges in 9 dimensions. Such supercharges are minimal (i.e. have 5d image).  They are stabilized by $\SU(4)$.  Like in 10 dimensions, the R-symmetry group is trivial, and so the twisted theory by such a supercharge is only $\ZZ/2\ZZ$-graded.

@@

\subsection{Dimension 8}
The 8-dimensional $\mc N=1$ super Yang-Mills theory is obtained by dimensional reduction of $\mc N=1$ super Yang-Mills from $\RR^{10}$ to $\RR^8$.  It has BRST fields given by a ghost, an 8d gauge field $A$, a pair of $\gg$-valued scalar fields $\phi_1$ and $\phi_2$, and a Dirac spinor field $\lambda = (\lambda_+, \lambda_-) \in S_+ \oplus S_-$.

In 8 dimensions, there are 3 classes of non-equivalent non-zero supercharges by which we can twist.
\begin{enumerate}
 \item Pure spinors, with $\lambda_+ = 0$ or $\lambda_- = 0$.  These supercharges are holomorphic.  They are stabilized by $\SU(4)$.  Twists by pure spinors can be made $\ZZ$-graded using a maximal torus in the R-symmetry group $\GL(1)$.
 \item Impure square-zero spinors with $\lambda_+ = 0$ or $\lambda_- = 0$.  These supercharges are topological.  They are stabilized by $\Spin(7) \sub \SO(8)$.  Again, twists by such supercharges can be made $\ZZ$-graded.
 \item Square-zero spinors where both $\lambda_+$ and $\lambda_-$ are non-zero.  Such supercharges have a 5-dimensional image in $\CC^8$.  Twists by such supercharges are still only $\ZZ/2\ZZ$-graded.
\end{enumerate}

When we dimensionally reduce the minimally twisted 10- or 9-dimensional super Yang-Mills theories to 8 dimensions we obtain either the twist by a supercharge of type 1, or of type 3, depending on whether we reduce along an invariant direction or a non-invariant direction. \chris{I should say this more clearly, maybe including some general discussion at the beginning of the section, and referring to the figure.}

\subsubsection{The Holomorphic Twist}

\subsubsection{The Topological Twist}

\subsubsection{The Rank 2 Twist}
